---
author: "LTC Melanie Vinton"
date: "March 16, 2017"
---

# ARGOS - YouTube

This R package provides data collection, cleaning, and visualization for YouTube data, accessed from the YouTube API.  

The first step is to get authorization credentials for a Google App account, such as Gmail or YouTube, at <https://console.developers.google.com/projectselector/apis/credentials>.  Then you need to authenticate using the OAuth 2.0 credentials (client ID and client secret) with the YouTube API using the *yt_oauth* function in the **tuber** package.  Eventually, I will add at function to this package to do this so that the **tuber** package is not necessary.

```{r eval=FALSE}
yt_oauth(client, secret)
```

## Outputs
Most of the functions provide an output in the form of a dataframe and saves that dataframe to a CSV file.  The user must have a folder called "yt_collection" in the working directory when the function is run, which is where the CSV file will be saved.  Otherwise, the functions will not execute properly.  The CSV files will be named by the type of function, input parameter (such as video ID), and date-time information for the system time when the function was run.  For example, a file may be named:  channel_ABCD_20170301_1400.csv, which means the user ran the yt.AllChannelVideos() function for channel ID "ABCD" at 1400 on 1 March 2017.

## Functions
The first thing to understand about YouTube is that it is a collection of videos and channels.  A channel is equivalent to a user or account, and generally includes multiple videos.  Each video has statistics including views, likes, dislikes, favorites, and comments.  Each channel has a channel ID and some have vanity names that replace the channel ID in the URL for that channel.  Every video has a video ID.

### yt.AllChannelVidoes()
The first function is to collect a list of all the videos from a channel, including the stats for each video.  This function allows you to set a date range for the collection using the "published_before" and "published_after" parameters.  Currently this function will only accept the channel ID, not channel vanity names.  A future update will take a vanity name and determine the channel ID.  This example collects all the videos from The Late Show with Steven Colbert channel during the first week of March 2017.
```{r eval=FALSE}
colbert <- yt.AllChannelVideos(channel_id = "UCMtFAi84ehTSYSE9XoHefig",
                               published_after = "2017-03-01T00:00:00Z",
                               published_before = "2017-03-07T00:00:00Z")
```
The results include 56 videos and the following information about each video:
video ID, date-time posted, channel ID, title, description, channel title, date collected, view count, like count, dislike count, favorite count, comment count, tags, and language.

### yt.search()
This function collect a list of videos related to a search term, regardless of channel, and can be limited by a date range.  This example collects videos related to "golf" in the first week of March 2017.
```{r echo = FALSE}
golf <- yt.search(term="golf", 
                  published_after = "2017-03-01T00:00:00Z",
                  published_before = "2017-03-07T00:00:00Z")
```
The results include 431 videos and the following information about each video:  video ID, date-time posted, channel ID, title, description, and channel title.


### yt.singleVideoInfo()
This function will provide statistics for a video.  The results include video ID, view count, like count, dislike count, favorite count, comment count, date collected, date-time posted, channel ID, title, description, tags, and category ID.  This example collects information on a video featuring Bubba the Bichon Frise.
```{r echo=FALSE}
bubba <- yt.singleVideoInfo(video_id = "tgchTz8XjrI")
```

### yt.related()
This function collects a list of up to 50 videos that are related to another video. 
```{r echo=FALSE}
bubba_rel <- yt.related(video_id = "tgchTz8XjrI")
```

